\chapter{Build Procedure} \label{appendixBuildProcedure}

This section is mainly for my own benefit and documents how to do a full build
(including building this report document) of the FencingArchive project.
\lstset{
    frame=single,
    breaklines=true,
    postbreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\color{black}\hookrightarrow\space}}
}
\lstdefinelanguage{bash}{
    keywords = {}
}
\begin{enumerate}
  \item Generate Javadocs
\begin{lstlisting}[language=bash, caption={Javadoc Generation}]
cd ~/workspace/FencingArchive
javadoc -d ./static/javadoc -sourcepath ./src/main/java net.fencingarchive
javadoc -d ./static/javadoc -sourcepath ./src/main/java sportsml
\end{lstlisting}
  \item Maven build of FencingArchive project (either versioned or not, deployed
  or not)
\begin{lstlisting}[language=bash, caption={Maven Build}]
mvn {clean} {release:update-versions} package {tomcat7:redeploy}
\end{lstlisting}
  \item Generate effective class diagrams
  \begin{enumerate}
    \item \label{objectAidDiagramStart} In Eclipse, navigate to
    TM470/src/ObjectAid and create new ObjectAid class diagram. All options should be selected, also select the option to save the diagram as png along with the ucls file.
    \item Drag and drop all of the \(.java\) files from the
    \(net.fencingarchive\) package into the newly-created diagram.
    \item \label{objectAidDiagramEnd} Move the classes such that relationships
    don't overlap classes or other relationships. Relationships can be re-routed by right-clicking on the
    relationship and selecting \(Auto Route\).
    \item Repeat stages \ref{objectAidDiagramStart} to
    \ref{objectAidDiagramEnd} for each package that a class diagram is needed
    for.
    \item Update \(models.tex\) to include all class diagram png files.
  \end{enumerate}
  \item Generate effective database ER diagram
  \begin{enumerate}
    \item Open MySQL Workbench and connect to the correct MySQL instance
    and database.
    \item Select \(Database\)-\(Reverse Engineer\)
    \item Follow the wizard.
    \item Rearrange the diagram to remove overlaps, if necessary. As much as
    possible, try to follow the layout of the associated class diagram to make
    for more straight-forward visual comparison.
  \end{enumerate}
  \item Make sure that \(source-code.tex\) contains all the source files that
  need to be included in the report.
  \item Download some output XML from the API to a local file to include in the
  final report. Make sure that this file is included in the relevant \(tex\)
  file.
\begin{lstlisting}[language=bash, caption={API Downloads}]
cd ~/workspace/TM470/...
wget -O event-1.xml http://127.0.0.1:8080/FencingArchive/api/event/1
\end{lstlisting}
\end{enumerate}
